---
title: "Peer-graded Assignment: Plotly chart"
author: "Federico Viscioletti"
date: "1/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the R Markdown document containing an interactive chart created using the **plotly** R library.

Let's see two examples of plotly charts. A scatterplot and a 2D heatmap

## Scatterplot

First I am going to plot a scatter chart using the **rmvnorm** method from the **mvtnorm** library. The method generates a vector of random values from an n-dimensional multivariate normal distribution.

```{r warning = F, message = FALSE}
# install.packages('mvtnorm')
library(plotly)

sigma_values <- matrix(c(0.9, -.80, -.80, 0.9), ncol = 2)
observations <- mvtnorm::rmvnorm(750, sigma = sigma_values)
chart <- plot_ly(x = observations[,1], y = observations[,2])

chart %>% add_markers(alpha = 0.4) %>% 
        layout(title = "Random Values from Multinormal Distribution",
               xaxis = list(title = "x values"),
               yaxis = list(title = "y values"))
```

## Heatmap

In this case we are going to represent the same data source with a 2D heatmap.

```{r}
chart <- plot_ly(x = observations[,1], y = observations[,2])

chart %>% add_histogram2d() %>%
        layout(title = "Random Values from Multinormal Distribution",
               xaxis = list(title = "x values"),
               yaxis = list(title = "y values"))
```


